Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-29 paper/gd1.tex
model stream

To compute initial conditions for the stream model, we fit an orbit to the
observed properties of the stream in a fixed model for the gravitational
potential of the Milky Way.
We use a three-component potential model to represent the Galaxy, consisting of
a Miyamoto-Nagai disk (\citealt{Miyamoto:1975}), a Hernqust bulge
(\citealt{Hernquist:1990}), and a spherical Navarro-Frenk-White dark matter halo
(\citealt{Navarro:1996}).
We set the disk scale-length parameters to closely match the disk model found in
\citet{Bovy:2015}, and other parameters are set to reproduce an approximately
flat rotation curve between $5 < R < 15~\kpc$ with a circular velocity at the
solar circle, $v_{\textrm{circ}, \odot} \approx 230~\kms$.

To initialize the model stream generation, we \todo{...}

Stream properties computed from resulting model stream are plotted in \figurename~\ref{fig:track-and-model} as \todo{XX}.

>>>>

To compute initial conditions for the stream model, we fit an orbit to the
observed properties of the stream in a fixed model for the gravitational
potential of the Milky Way.
We use a three-component potential model to represent the Galaxy, consisting of
a Miyamoto-Nagai disk (\citealt{Miyamoto:1975}), a Hernquist bulge
(\citealt{Hernquist:1990}), and a spherical Navarro-Frenk-White dark matter halo
(\citealt{Navarro:1996}).
We set the disk scale-length parameters to closely match the disk model found in
\citet{Bovy:2015}, and other parameters are set to reproduce an approximately
flat rotation curve between $5 < R < 15~\kpc$ with a circular velocity at the
solar circle, $v_{\textrm{circ}, \odot} \approx 230~\kms$.

To initialize the model stream generation, we assume that the present day (i.e.
final) position of the progenitor system is at $\phi_1 = XX^\circ$.
We integrate backwards for $4~\textrm{Gyr}$ using the orbital parameters at this
location using the Leapfrog integration scheme with a timestep of
$0.5~\textrm{Myr}$, then begin the model stream generation using the Lagrange
point stripping method discussed above.
Stream particles are release at each timestep of the progenitor orbit
integration, resulting in 16,000 stream particles by the end of the model stream
generation.
We assume an initial progenitor mass of $M=10^5~\msun$, and linearly decrease
the mass of the progenitor until present day, where we assume $M = 0~\msun$
(i.e. fully disrupted).
Stream properties computed from this resulting model stream are plotted in
\figurename~\ref{fig:track-and-model} as \todo{XX}.
